---
title: "Assignment1024"
author: "Suz"
date: '2019 10 24 '
output:
  word_document: default
  html_document:
    df_print: paged
---
1) Children's IQ scores are normally distributed with a mean of 100 and a standard deviation of 15. What proportion of children are expected to have an IQ between 80 and 120?

mean=100
std=15
lowerbound=80
upperbound=120

```{r}
#probability from a normal distribution
mean=100
std=15
lowerbound=80
upperbound=120

pnorm(upperbound, mean, std, lower.tail=TRUE)- pnorm(lowerbound, mean, std, lower.tail=TRUE)
```


2) Generate data for hypothesis testing (student's T-test) and show me one exmaple each of a significant result and a non-significant result. Explain your thinking.


Data from: http://fcon_1000.projects.nitrc.org/indi/adhd200/

```{r}
raw_adhd<-read.csv(file="adhd200.csv")
df_adhd<-data.frame(raw_adhd)
an_children<-df_adhd[df_adhd$DX != "pending",] #disregard pending diagnosis
girls<-an_children[an_children$Gender==0,]
girls_not<-girls[girls$DX==0,]
girls_diagnosed <- girls[girls$DX!=0,]
boys<-an_children[an_children$Gender==1,]
boys_not<-boys[boys$DX==0,]
boys_diagnosed <- boys[boys$DX!=0,]


#girls_diagnosed
#boys_diagnosed

boys_age <-boys_diagnosed$Age
girls_age<-girls_diagnosed$Age

```

T test for the age of girls and boys who were diagnosed:

```{r}
res1<-t.test(boys_age, girls_age, var.equal = TRUE)
res1
```

Significance of comparing the age of girls and boys who were diagnosed:
```{r}
res1$p.value < 0.05
```
This implies that the difference between the mean of the two dataset can be significant. However, shapiro test showed that the boys data was not normally distributed, which could show a wrong result.


T test for the age boys who were diagnosed with adhd or boys who were not:

```{r}
res2<-t.test(boys_not$Age, boys_diagnosed$Age, var.equal=TRUE)
res2
```

Significance of comparing the age of boys diagnosed with adhd, and typical for age:
```{r}
res2$p.value <0.05
```
This implies that the difference between the ages of boys who were diagnosed and who were not is not siginificant, which is most likely the result of using a dataset that was focusing on a certain age interval of children. 


