---
title: "Assignment1114"
author: "Suz"
date: '2019 11 7 '
output: html_document
---
 	
1. Create a prediction hypothesis
2. Find data related to the prediction
3. Clean the data and get it ready for R Studio


Data from: http://fcon_1000.projects.nitrc.org/indi/adhd200/

Hypothesis: Children who were diagnosed with Combined/Hyperactive-Impulsive ADHD are likely to be diagnosed at an earlier age than Inattentive type of ADHD.

Diagnosis(DX) code:
0 Typically Developing Children 
1 ADHD-Combined
2 ADHD-Hyperactive/Impulsive
3 ADHD-Inattentive

```{r}
raw_adhd<-read.csv(file="adhd200.csv")
df_adhd<-data.frame(raw_adhd)
children<-df_adhd[df_adhd$DX != "pending",] #disregard pending diagnosis

colnames(children)
```


T test for the age of children who were diagnosed with different types of ADHD:
```{r}
hyper_impulsive <- children[(children$DX==1 | children$DX==2),]
inattentive <- children[children$DX==3,]

#hyper_impulsive
#inattentive
res <- t.test(hyper_impulsive$Age, inattentive$Age)
res
```

Significance of comparing the age of children who were diagnosed with Combined/Hyperactive-Impulsive or Inattentive:
```{r}
res$p.value < 0.05
```

This implies that the difference between the mean of the two dataset is not significant. 


```{r}
res2 <- t.test(hyper_impulsive$Gender, inattentive$Gender)
res2$p.value
```



