---
title: "Assignment1114"
author: "Suz"
date: '2019 11 14 '
output:
  pdf_document: default
  html_document: default
---

#show equation
#don't show code for summary >> {r echo=FALSE}


Dependant Variable (Response): mpg
Independant Variables (Predictor): disp, hp, wt

First to look into the relationship between the variables we look into the plots:

```{r echo=FALSE}
plot(mpg~disp+hp+wt, data=mtcars)
```

From this, we can assume that mpg and the other variables are in a negative relationship.
Next we create a linear model regression with the variables, with mpg as the response variable to see how much each variables contribute in predicting mpg.

```{r}
stp1<-lm(mpg~disp+hp+wt, data=mtcars)
```

The summary:
```{r echo=FALSE}
summary(stp1)
```

The mathematical equation for this is:

mpg = 37.105505 + (-0.000937) * disp + (-0.031157) * hp + (-3.800891) * wt

With this equation we are able to predict the mileage per gallon depending on the disp, hp, wt variables.

However, as disp does not have a significance under 0.05, we leave it out in the next step.

```{r}
stp2<-lm(mpg~hp+wt, data=mtcars)
```

The summary:
```{r echo=FALSE}
summary(stp2)
```


Both variables have a significance level of 99% (p-value < 0.01).

Now we will see how much the variables effect mpg not individually but paired.

```{r}
stp3<-lm(mpg~hp*wt,data=mtcars)
```

The summary:
```{r echo=FALSE}
summary(stp3)
```

We can see that hp and wt together have a positive relationship to mpg, but the significance level is lower than when calculated individually.
Therefore, the interaction between hp and wt can be statistically less significant to consider into the equation.

The final equation of step 3 model looks like this:

mpg = 49.80 + (-0.12010)* hp + (-8.21662) * wt + (0.02785) *(hp:wt)

A change in the value of wt would make the biggest change in the value of mpg.



